Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-04 SupportingInformation.Rmd
small formatting change

 #atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$",
 #                               "$\\Ps_{0,0.1}-\\Ps_{0.9,1}$",
 #                               "$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
 atdres<-data.frame(Statistic=c("$\\cor_{first.slice}-\\cor_{last.slice}$",
                               "$\\Ps_{first.slice}-\\Ps_{last.slice}$",
                                "$\\Dsq_{last.slice}-\\Dsq_{first.slice}$"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)

>>>>

 #atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$",
 #                               "$\\Ps_{0,0.1}-\\Ps_{0.9,1}$",
 #                               "$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
 atdres<-data.frame(Statistic=c("$\cor_{\text{first slice}}-\cor_{\text{last slice}}$",
                               "$\\Ps_{first.slice}-\\Ps_{last.slice}$",
                                "$\\Dsq_{last.slice}-\\Dsq_{first.slice}$"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)
